Litrepl: Literate Paper Processor Promoting Transparency More Than Reproducibility

### 2025-01-05 paper/paper.tex
Update paper

Following \textcite{Vallet2022}, we suggest changing the focus of human-computer
interaction towards simplicity and transparency. We saw an opportunity to
implement a tool that would offer REPL-style editing, be compatible with
existing code editors and text formats, thus maintaining familiar editing
practices, contain no important hidden state variables and have a significantly
smaller codebase.

@@

In Litrepl, these details are hardcoded for several prominent interpreter
families, which we refer to as \textit{interpreter classes}. At the time of
writing, Litrepl supports three such classes: \texttt{python}, \texttt{sh}, and
\texttt{ai}. Using these names in command line arguments, users can configure
how to map code section labels to the correct class and specify which
interpreter command to execute to start a session for each class. For example,
to select a Bourne-Again Shell interpreter as \verb|sh|, we add the
\verb|--sh-interpreter=/usr/bin/bash| argument assuming that this binary is
present in the system.
%lnoresult

>>>>

Following \textcite{Vallet2022}, we suggest changing the focus of human-computer
interaction towards simplicity and transparency. We saw an opportunity to
implement a tool that would offer REPL-style editing, be compatible with
existing code editors and text formats, thus maintaining familiar editing
practices, contain only a few hidden state variables, and have a significantly
smaller codebase.

@@

In Litrepl, these details are hardcoded for several prominent interpreter
families, which we refer to as \textit{interpreter classes}. At the time of
writing, Litrepl supports three such classes: \texttt{python}, \texttt{sh}, and
\texttt{ai}. Using these names in command line arguments, users can configure
how to map code section labels to the correct class and specify which
interpreter command to execute to start a session for each class. For example,
to select a Bourne-Again Shell interpreter as \verb|sh|, we add the
\verb|--sh-interpreter=/usr/bin/bash| argument assuming that this binary is
present in the system.
